A boundary integral equation approach to computing eigenvalues of the Stokes operator

### 2019-05-07 doc/draft-01/01intro.tex
Updating buckling eigenvalues paper

Consider the pure bending of an isotropic and homogeneous thin clamped
plate. 
Let $\Omega$ denote the midline of the plate, $\Gamma$ denote the 
boundary of $\Omega$ and $w$ denote the vertical displacement.
The buckling problem consists of finding 
values $k^{2}$ such that the boundary value problem

\begin{align}
\Delta (\Delta + k^2) w &= 0 \quad \textrm{in} \quad \Omega \label{eq:buck1} \; , \\
w &= 0 \quad \textrm{on} \quad \Gamma \label{eq:buck2} \; ,\\
\dwdn &=0 \quad \textrm{on} \quad \Gamma \label{eq:buck3} 
\end{align}
has a non-trivial solution. In a slight abuse of notation,
these values and the corresponding solutions are often
referred to as ``eigenvalues'' and ``eigenfunctions'',
respectively. 
It is well known that the buckling problem has a
countable collection of such values
$0 < k_{1}^{2} \leq k_{2}^2 \leq \ldots \uparrow \infty$,
counting multiplicites.

\begin{remark}
  When $k = i\alpha$, the differential equation
  \cref{eq:buck1} is known as the modified biharmonic
  equation. As there appears to be no preferred
  name for the equation with real-valued $k$,
  we will refer to \cref{eq:buck1} as the
  Helmholtz-biharmonic equation.
\end{remark}

@@

Numerical simulations have long played an important
role in the analyses described above and there are a number
of available methods (note that some of the references
included here are written in terms of the related
Stokes eigenvalue problem, which has equivalent
eigenvalues on simply connected domains). We do not
seek to review the literature here but will provide
some context for the present work. Finite element methods
are ubiquitous in mechanical engineering applications
and are flexible with respect to both the governing
equations and the shape of the domain. Such a method
would first obtain a ``weak'' form of the equations
\cref{eq:buck1,eq:buck2,eq:buck3} and then 
approximate the solution space in some
finite dimensional basis, resulting in a discrete model
for the buckling problem.
The eigenvalues $k^2$ are then
approximated by the eigenvalues of the discrete
model \cite{johnson1974beam,rannacher1979nonconforming,
  jia2009approximation,carstensen2014guaranteed}.
Because of the fourth order term in \cref{eq:buck1},
the system matrices resulting from a finite element
discretization can have large condition numbers (growing
like $1/h^4$ where $h$ is the diameter of a typical element
in the discretization) which can cause numerical instability.

Integral equation methods \cite{kress1989linear,
  atkinson2009numerical,kitahara2014boundary} present
a natural alternative to the finite element method
for the buckling problem, because (a) the
integral representation acts as an analytical preconditioner
for the fourth order term and (b) the problem is reduced
to one defined on the boundary of the domain alone,
requiring fewer degrees of freedom to resolve the solution
on a complex domain. In an integral equation method,
the solution $w$ is represented in terms of a sum of
two layer potentials (which a priori satisfy
\cref{eq:buck1}) with unknown densities. Substituting this
representation into the boundary conditions
\cref{eq:buck2,eq:buck3} results in an integral equation
for the unknown densities, which
is in turn discretized using numerical quadrature.
Unlike the original equation \cref{eq:buck1} and the weak
formulation used in a finite element method, the integral
equation for the unknown densities has a nonlinear dependence
on the parameter $k^2$. In an integral equation method, then,
the eigenvalues are found by searching for the values
of $k^2$ where the discrete system for the unknown densities
is no longer invertible.

While integral equation methods for the buckling problem
have been considered previously, the existing formulations
have resulted in first kind integral equations, i.e. equations
in which the operator is compact \cite{kitahara2014boundary,
  antunes2011buckling}. This is unsatisfying from a theoretical
perspective, because such operators are never invertible
(though, they are injective precisely when $k^2$ is an
eigenvalue \cite{kitahara2014boundary}) so that the
relation between the non-invertibility of the discrete system
and the eigenvalues is obscured. Further, such representations
create numerical challenges because common measures of the
``non-invertibility'' of a matrix, like the smallest singular
value or the determinant, converge rapidly to zero for all
values of $k^2$ as the boundary is refined.

Second kind integral equations, i.e. integral equations
of the form $\mathcal{I} + \mathcal{K}$ where $\mathcal{K}$
is compact, have a more satisfying theory
\cite{reed1972methods}, which translates
well to numerical implementation
\cite{bornemann2010numerical,zhao2015robust}.
In \cite{zhao2015robust}, Zhao and Barnett demonstrated
that the eigenvalues of the drum problem can be
computed with such a framework, resulting in
spectrally accurate numerical methods.
In this paper, we develop a second kind integral
equation for the buckling problem, based on the
approach in \cite{rachh2017integral}. This allows
for a robust approach to computing the eigenvalues
of the buckling problem, model after the approach for
the drum problem in \cite{zhao2015robust}, which we
demonstrate with a number of examples.

>>>>

Consider the pure bending of an isotropic and homogeneous thin clamped
plate. 
Let $\Omega$ denote the midline of the plate, $\Gamma$ denote the 
boundary of $\Omega$ and $w$ denote the vertical displacement.
The buckling eigenvalue problem consists of finding 
values $k^{2}$ such that the boundary value problem

\begin{align}
\Delta (\Delta + k^2) w &= 0 \quad \textrm{in} \quad \Omega \label{eq:buck1} \; , \\
w &= 0 \quad \textrm{on} \quad \Gamma \label{eq:buck2} \; ,\\
\dwdn &=0 \quad \textrm{on} \quad \Gamma \label{eq:buck3} 
\end{align}
has a non-trivial solution $w$. 
It is well known that the values $k^2$ are necessarily real 
and positive and there is a countable collection
of such values 
$0 < k_{1}^{2} \leq k_{2}^2 \leq \ldots \uparrow \infty$,
counting multiplicites.

\begin{remark}
  When $k = i\alpha$, the differential equation
  \cref{eq:buck1} is known as the modified biharmonic
  equation. As there appears to be no preferred
  name for the equation with real-valued $k$,
  we will refer to \cref{eq:buck1} as the
  oscillatory biharmonic equation.
\end{remark}

@@

A related problem is that of the Stokes eigenvalue problem
which is to find values $k^2$ such that
\begin{align}
\Delta (\Delta + k^2) w &= 0 \quad \textrm{in} \quad \Omega \label{eq:stokes1} \; , \\
\nabla w &= 0 \quad \textrm{on} \quad \Gamma \label{eq:stokes2} \; ,\\
\end{align}
has a non-trivial solution $w$.
While the buckling eigenvalues are identical to the Stokes
eigenvalues on simply connected domains, on multiply
connected domains it turns out that the buckling eigenvalues
are a subset of the Stokes eigenvalues.

In this note, we derive integral conditions on the stream function 
associated with the Stokes eigenfunction
to determine whether the Stokes eigenvalue is also a 
buckling eigenvalue on multiply connected domains.
Thus, given the Stokes eigenvalues 
of the domain and the stream functions associated with the 
corresponding eigenfunctions, 
the buckling eigenvalues can be determined using a simple
post-processing step.
Given $k^2$ to be a Stokes eigenvalue, we also derive
a well-conditioned second-kind integral equation for computing 
the stream function associated with the 
Stokes eigenfunction.

Numerical simulations have long played an important
role in the analyses described above and there are a number
of available methods (note that some of the references
included here are written in terms of the related
Stokes eigenvalue problem, which has equivalent
eigenvalues on simply connected domains). We do not
seek to review the literature here but will provide
some context for the present work. Finite element methods
are ubiquitous in mechanical engineering applications
and are flexible with respect to both the governing
equations and the shape of the domain. Such a method
would first obtain a ``weak'' form of the equations
\cref{eq:buck1,eq:buck2,eq:buck3} and then 
approximate the solution space in some
finite dimensional basis, resulting in a discrete model
for the buckling problem.
The eigenvalues $k^2$ are then
approximated by the eigenvalues of the discrete
model \cite{johnson1974beam,rannacher1979nonconforming,
  jia2009approximation,carstensen2014guaranteed}.

\note{needs work}

### 2019-05-07 doc/draft-01/02prelim.tex
Updating buckling eigenvalues paper

\section{Mathematical Preliminaries}

In this paper, vector-valued
quantities are denoted by bold, lower-case letters
(e.g. $\bh$), while tensor-valued quantities are bold
and upper-case (e.g. $\mathbf{T}$). 
Subscript indices of non-bold characters (e.g. $h_j$ or $T_{jkl}$)
are used to denote the entries within a vector ($\bh$) or tensor ($\bT$).
We use the standard Einstein summation convention; in other words, 
there is an implied sum taken over the repeated indices of 
any term (e.g. the symbol $a_{j} b_{j}$ is used to represent the sum
$\sum_{j} a_{j} b_{j}$).
If $\xx = (x_1,x_2)^\intercal$, then $\xx^\bot = (-x_2,x_1)^\intercal$.
Similarly, $\nabla^\bot = (-\partial_{x_2},\partial_{x_1})^\intercal$.
Upper-case script characters (e.g. $\mathcal{K}$) are reserved for
operators on Banach spaces, with $\mathcal{I}$ denoting the
identity.

\subsection{Green's functions}

Let $\mathcal{L}_x$ denote a linear differential operator. A fundamental
solution $G(\xx,\yy)$ of $\mathcal{L}_x$ satisfies the equation
$\mathcal{L}_x G(\xx,\yy) = \delta_y(\xx)$ in the distributional sense, i.e.
for sufficiently smooth $f$
\begin{equation}
  \mathcal{L}_x \int_{\R^2} G(\xx,\yy) f(\yy) \, dy = f(\xx) \; .
\end{equation}
We consider here
``free-space'' Green's functions, i.e. fundamental solutions which satisfy
some natural growth or decay conditions as $|\xx-\yy| \to \infty$.
The Green's function of the oscillatory biharmonic equation
\cref{eq:buck1} is given by 
\begin{equation}
  \Gbh(\xx,\yy) = \frac{1}{k^2}
  \left (\frac{1}{2\pi} \log |\xx-\yy| +
  \frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \right ) \, , 
\end{equation}
where $k$ is the Helmholtz paramater in the oscillatory biharmonic equation,
and $H_{0}^{1}(r)$ is the Hankel function of the first kind of order zero.
Note that this is a scaled difference of the Green's function for
Laplace, i.e.

\begin{equation}
  \Glap(\xx,\yy) = \frac{1}{2\pi} \log |\xx-\yy| \; ,
\end{equation}
and the Green's function for the Helmholtz equation

\begin{equation}
  \Ghelm(\xx,\yy) = -\frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \; .
\end{equation}

\subsection{An integral representation for the Stokes eigenvalue
  problem}

The Stokes eigenvalue problem (with ``no-slip'' boundary conditions)
seeks values $k^2$ such that the equations
\begin{align}
  \nabla p - \Delta \uu - k^2 \uu &= 0 \quad \textrm{in} \quad \Omega
  \; , \label{eq:helmstokes}\\
  \nabla \cdot \uu &= 0 \quad \textrm{in} \quad \Omega
  \; , \label{eq:helmstokescty} \\
  \uu &= 0 \quad \textrm{on} \quad \Gamma \; \label{eq:helmstokesnoslip}
\end{align}
have a non-trivial solution. In the case that $k=i\alpha$ for
some real-valued $\alpha$, the equations \cref{eq:helmstokes,eq:helmstokescty}
are known as the modified Stokes equations and are of particular
interest for their application to numerical simulations of unsteady
flow
\cite{pozrikidis1992boundary,biros2002embedded,jiang2013second}.
In the absence of a preferred name for the case of real-valued $k$,
we will refer to \cref{eq:helmstokes,eq:helmstokescty} as the
oscillatory Stokes equations.

\subsubsection{Stokeslets and stresslets}

In this section, we review the derivation of the
modified Stokeslet, but for the imaginary parameter
regime, which is the appropriate setting for the Stokes
eigenvalue problem.
The original modified Stokeslet is more well known,
and is of particular interest for its application to
numerical simulations of the unsteady Stokes equations
\cite{pozrikidis1992boundary,biros2002embedded}.

 Consider the solution of
\cref{eq:helmstokes,eq:helmstokescty} where a $\delta$-mass
centered at $\yy$ with strength $\ff$
has been added to the right-hand side of \cref{eq:helmstokes}, i.e.

\begin{align}
  \nabla p - \Delta \uu - k^2 \uu &= \delta_\yy \ff \; ,
  \label{eq:helmstokes_charge} \\
  \nabla \cdot \uu &= 0 \; .
\end{align}
Recall that

\begin{equation}
 \Delta \Glap(\xx,\yy) = \delta_\yy(\xx) \; .
\end{equation}
If we substitute this expression into
\eqref{eq:helmstokes_charge} and take the divergence,
we obtain

\begin{equation}
  p = \nabla \Glap(\xx,\yy) \cdot \ff \; .
\end{equation}
We then have, formally,

\begin{align}
  \uu &= - (\Delta + k^2)^{-1} ( \Delta \Glap \ff
  - \nabla (\nabla \Glap \cdot \ff ) ) \\
  &= \left ( -\Delta + \nabla \otimes \nabla \right )
  \Gbh \ff \; .
\end{align}
The tensor

\begin{equation} \label{eq:stokeslet}
  \GG = - \II \Delta \Gbh + \nabla \otimes \nabla \Gbh
\end{equation}
is then the equivalent of a Stokeslet
\cite{pozrikidis1992boundary} for the problem
\eqref{eq:helmstokes}.

A related object is the stresslet, which is defined
in terms of the stress tensor of a velocity, pressure
pair induced by a Stokeslet. For these tensors, we find
that it is more convenient to express them in index notation
with the Einstein index summing convention.
Recall that the stress tensor $\bsigma$ is defined as

\begin{equation}
  \sigma_{ij} = -p \delta_{ij} + \left ( \partial_{x_j}u_i
  +\partial_{x_i} u_j \right ) \; ,
\end{equation}
where $\delta_{ij}$ is the standard Kronecker delta notation.
The stresslet $\TT$ is defined to be

\begin{align}
  T_{ijk} &= - \partial_{x_j} \Glap \delta_{ik}
  + \partial_{x_k} \left ( -\Delta \Gbh \delta_{ij} +
  \partial_{x_i} \left(\partial_{x_j} \Gbh \right) \right)
  \nonumber \\
  & \qquad+ \partial_{x_i} \left ( -\Delta \Gbh \delta_{kj} +
  \partial_{x_k} \left(\partial_{x_j} \Gbh \right) \right)
  \; .
\end{align}
Let $u_i = G_{ij} f_j$ and $p = \partial_{x_i} \Glap f_i$ be a
solution of the Stokes equations induced by a Stokeslet.
Then the corresponding stress tensor is given by
$\sigma_{ik} = T_{ijk} f_j$.

For the layer potentials of the next section, the following
formulas are useful. Let $\bnu$ be a given vector. When
summing over the third index, we obtain

\begin{equation}
  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla \Glap
  + \partial_\nu \left ( -\Delta \Gbh \II
  + \nabla \otimes \nabla \Gbh \right)
  + \nabla \otimes \left ( -\Delta \Gbh \bnu
  + \partial_{\nu} \nabla \Gbh \right) \; .
\end{equation}
%\begin{align}
% -\Delta \Gbh \bnu
% + \partial_{\nu} \nabla \Gbh &=
% ( (-\partial_{x_1x_1}-\partial_{x_2x_2}) \nu_1 \Gbh +
% (\partial_{x_1x_1}\nu_1 + \partial_{x_2x_1} \nu_2 )\Gbh,
% (-\partial_{x_1x_1}-\partial_{x_2x_2}) \nu_2 \Gbh +
% (\partial_{x_1x_2}\nu_1 + \partial_{x_2x_2} \nu_2 )\Gbh) \\
% &= (-\partial_{x_2} \partial_\tau \Gbh,
% \partial_{x_1} \partial_\tau \Gbh)
%\end{align}
%\begin{equation}
%  \begin{pmatrix}
%    -\partial_{x_2x_2} & \partial_{x_1x_2} \\
%    \partial_{x_1x_2} & -\partial_{x_1x_1}
%  \end{pmatrix} = -\nabla^\bot \otimes \nabla^\bot
%\end{equation}
Let $\btau = \bnu^\bot$. Then

\begin{equation}
  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla \Glap
  - \nabla^\bot \otimes \nabla^\bot \partial_\nu \Gbh
  +\nabla \otimes \nabla^\bot \partial_\tau \Gbh \; .
\end{equation}

\subsubsection{Layer potentials and integral representation}

We now use the Stokeslet and stresslet definitions
of the previous section to define the standard single
and double layer potentials of the Stokes eigenvalue
problem. The single layer potential is defined to
be

\begin{equation}
  \SS \bmu (\xx) = \int_\Gamma \GG (\xx,\yy) \bmu(\yy)
  \, dS(\yy) \; .
\end{equation}
The double layer potential is defined to be

\begin{equation} \label{eq:doublelayer}
  \DD \bmu (\xx) = \int_\Gamma \left ( \TT_{\cdot,\cdot,k}\nu_k(\yy)
  \right )^\intercal \bmu(\yy) \, dS(\yy) \; ,
\end{equation}
where $\bnu$ denotes the outward unit normal to the boundary.
If we write $\bmu = \bnu \mu_\nu + \btau \mu_\tau$,
where $\btau = \bmu^\bot$ is the positively oriented unit
tangent to the curve, then we have

\begin{align} \label{eq:stokesdlkernel}
  \left ( \TT_{\cdot,\cdot,k}\nu_k(\yy) \right )^\intercal
  \bmu(\yy) &= \left ( - \nabla \Glap(\xx,\yy) + 2 \nabla^\bot
  \partial_{\nu\tau} \Gbh(\xx,\yy) \right ) \mu_\nu(\yy) \nonumber \\
  & \qquad+
  \nabla^\bot \left (\partial_{\tau\tau}-\partial_{\nu\nu} \right )
  \Gbh(\xx,\yy) \mu_\tau(\yy) \; .
\end{align}

>>>>

\section{Mathematical Preliminaries}
\label{sec:prelim}
In this paper, vector- and tensor-valued quantities
are denoted by bold letters (e.g. $\bh$ and $\mathbf{T}$). 
Subscript indices of non-bold characters (e.g. $h_j$ or $T_{ij\ell}$)
are used to denote the entries within a vector or tensor.
We use the standard Einstein summation convention; i.e., 
there is an implied sum taken over the repeated indices of 
any term (e.g. the symbol $a_{j} b_{j}$ is used to represent the sum
$\sum_{j} a_{j} b_{j}$).
If $\xx = (x_1,x_2)^\intercal$, then $\xx^\bot = (-x_2,x_1)^\intercal$.
Similarly, $\nabla^\bot = (-\partial_{x_2},\partial_{x_1})^\intercal$.
Upper-case script characters (e.g. $\mathcal{K}$) are reserved for
operators on Banach spaces, with $\mathcal{I}$ denoting the
identity. Given a set $X$, we denote the closure of $X$
by $\overline{X}$.

In the rest of the paper, 
suppose that $\Omega$ is a multiply connected region defined by
the intersection of a simply connected domain $\Omega_{0}$ 
and the exteriors of a finite collection of bounded
simply connected domains $\{ \Omega_{i} \}_{i=1}^{m}$. 
Let $\Gamma_{i}$, denote the boundary of $\Omega_{i}$, and 
let $\Gamma = \cup_{i=0}^{m} \Gamma_{i}$ denote the boundary of $\Omega$.
Let $\bnu(\bx)$ denote the outward normal at $\bx \in \Gamma$.

\section{Stokes eigenvalue problem}
The Stokes Dirichlet eigenvalue problem is to find values $k^2$ such that
\begin{equation}
\begin{aligned}
  -\Delta \uu + \nabla p &= k^2 \uu \quad \textrm{in} \quad
  \Omega \label{eq:ostokes} \; , \\
  \nabla \cdot \uu &= 0 \; , \\
  \bu &=0 \quad \textrm{on} \quad \Gamma \, ,
\end{aligned}
\end{equation}
has a non-trivial solution $(\bu,p)$.
Since the Stokes eigenfunction $\bu$ is divergence free, 
and satisfies 
$\int_{\Gamma_{i}} \bu \cdot \bnu \, ds = 0$ 
for all $i=0,1,2\ldots m$, there exists a single valued
stream function $\psi$ associated with $\bu$, i.e., 
$\bu = \nabla^{\perp} \psi$ for all $\bx \in \Omega$.

The Stokes eigenvalue problem can be reformulated as a buckling
eigenvalue problem with gradient boundary conditions for
the stream function $\psi$.
Plugging in $\bu = \nabla^{\perp} \psi$ and applying $\nabla^{\perp} \cdot$
to~\cref{eq:ostokes}, we observe that $\psi$ satisfies the following 
differential equation.

\begin{equation}
\begin{aligned}
\Delta (\Delta + k^2) \psi &= 0 \, \quad \textrm{in} \quad \Omega \, , \\
\nabla \psi &=0 \, ,\quad \textrm{in} \quad \Gamma \, .
\end{aligned}
\end{equation}

\section{Connection to buckling eigenvalues}
It is clear that if $w$ is a buckling eigenfunction with
eigenvalue $k^2$, then $\bu = \nabla^{\perp} w$ is a Stokes eigenfunction
with the same eigenvalue. 
Thus, for a given region $\Omega$,
the buckling eigenvalues are a subset of the Stokes eigenvalue.

However, the converse is not necessarily true. 
The reason is the following.
As before, suppose that $\bu$ is a Stokes eigenfunction
with eigenvalue $k^2$.
Note that a single valued stream function $\psi$ associated with
$\bu$ always exists. 
Moreover, on each component $\Gamma_{i}$, 
$\psi$ satisfies $\partial_{\tau} \psi = 0$, which implies that
$\psi$ is a constant on $\Gamma_{i}$, for each $i=0,1,2\ldots m$.
If the domain is simply connected, then since $\psi$ is only
well-defined upto a constant, we can adjust to constant term 
to ensure that $\psi$ also satisfies $\psi = 0$ on $\Gamma_{0}$.
However, on multiply connected domains, this is not always 
the case since $\psi$ might be different constants on different
boundary components. 
In the following lemma, we identify necessary and sufficient 
conditions on the stream function $\psi$ to guarantee that
$\psi$ (upto a constant) is also a buckling eigenfunction.

\begin{lem}
\label{lem:mainlem}
Suppose that $k^2$ is a Stokes eigenvalue for the region $\Omega$ and 
let $\bu$ be the corresponding eigenfunction. 
Then, the stream function associated with the velocity $\bu$ defined by
$\psi = \left(\nabla^{\perp} \right)^{-1} \bu$ exists and is single valued. 
Furthermore, $k^2$ is also a buckling eigenvalue if and only if
there exists a constant $c$ such that
\begin{equation}
\frac{1}{\Gamma_{j}}\int_{\Gamma_{j}} \psi\, ds = c \quad \forall j=0,1,\ldots m \, .
\end{equation}
\end{lem}

\begin{proof}
Since $\bu$ is a Stokes eigenfunction, it satisfies
\begin{equation}
\int_{\Gamma_{j}} \bu \cdot \bn ds = 0 \quad j=1,2\ldots n \, .
\end{equation}
Thus, there exists a single valued stream function associated with the
velocity field $\bu$ such that 
\begin{equation}
\nabla^{\perp} w = \bu \, .
\end{equation}
Furthermore, since $\bu$ satisfies the oscillatory Stokes equations, 
$w$ satisfies
\begin{align}
\Delta (\Delta + k^{2} ) w &= 0 \, , \quad \bx \in \Omega \\
\nabla^{\perp} w = \bu &=0 \, ,\quad \bx \in \Gamma \, ,
\end{align}
In particular $\psi= c_{j}$ for $\bx \in \Gamma_{j}$ for
some constant $c_{j}$.
Thus $k$ is also a buckling eigenvalue if and only if 
\begin{equation}
c_{j} = \frac{1}{|\Gamma_{j}|}\int_{\Gamma_{j}} w ds =  c \, .
\end{equation}
The buckling eigenfunction is then given by $\psi -c$. 
\end{proof}

\section{Computing the stream function}
Given $k^2$ to be a Stokes eigenvalue, in this section, we describe
an integral formulation for computing the eigenfunction $\bu$
and the corresponding stream function $\psi$.

Following the approach in~\cite{askhameig2019}, we
first reformulate the oscillatory Stokes equation
as an integral equation on the boundary using the combined
field representation.

Let $\GG(\bx,\by)$ denote the Stokeslet for the oscillatory
Stokes equation and $T_{ij\ell}(\bx,\by)$ denote the corresponding
Stresslet. 
These are given by the formulae
\begin{align} 
  \GG &= - \II \Delta \Gbh + \nabla \otimes \nabla \Gbh 
\label{eq:ostokeslet} \\
  T_{ij\ell} &= - \partial_{x_j} \Glap \delta_{i\ell}
  + \partial_{x_\ell} \left ( -\Delta \Gbh \delta_{ij} +
  \partial_{x_i} \left(\partial_{x_j} \Gbh \right) \right)
  \nonumber \\
  & \qquad+ \partial_{x_i} \left ( -\Delta \Gbh \delta_{\ell j} +
  \partial_{x_\ell} \left(\partial_{x_j} \Gbh \right) \right)
  \; . \label{eq:ostress} 
\end{align}
$\Gbh$ is the Green's function for the oscillatory
biharmonic equation given by
\begin{equation}
  \Gbh(\xx,\yy) = \frac{1}{k^2}
  \left (\frac{1}{2\pi} \log |\xx-\yy| +
  \frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \right ) \, ,
  \label{eq:Gbh}
\end{equation}
where $k$ is the Helmholtz parameter in the oscillatory biharmonic equation,
and $H_{0}^{1}(r)$ is the Hankel function of the first kind of order zero,
and $\Glap(\xx,\yy)$ is the Laplace Green's function given by
\begin{equation}
  \Glap(\xx,\yy) = \frac{1}{2\pi} \log |\xx-\yy| \; . \nonumber
\end{equation}

Given a density $\bmu$, the oscillatory Stokes single and double layer
potentials denoted by $\bS[\bmu](\bx)$ and $\bD[\bmu](\bx)$ respectively,
are given by
\begin{align} \label{eq:singlelayer}
  \bS [\bmu] (\xx) &= \int_\Gamma \GG (\xx,\yy) \bmu(\yy)
  \, dS(\yy) \; , \\
  \bD [\bmu] (\xx) &= \int_\Gamma \left ( \TT_{\cdot,\cdot,\ell}(\xx,\yy)
  \nu_\ell(\yy)\right )^\intercal \bmu(\yy) \, dS(\yy) \; .
\end{align}
When solving the velocity boundary value problem for the oscillatory
Stokes equation on multiply connected domains, the velocity
is represented as a bomcinbed field layer potential, i.e.
setting $\bu = (i\eta \bS_{k} + \bD_{k})[\bmu]$, where
$\eta>0$ is a constant and $\bmu$ now is an unknown density.
By construction, this velocity field satisfies the oscillatory
Stokes equation.
On imposing the velocity boundary condition, and using the jump
conditions for the layer potentials (see~\cref{askhameig2019}, 
for example)
we obtain the following integral equation for the unknown density
$\bmu$,
\begin{equation}
\label{eq:inteq0}
(\cI - 2\cD_{k} -2i \eta \cS_{k})\bmu = 0 \, \quad \textrm{on} \quad \Gamma \,,
\end{equation}
where $\cS_{k}$ and $\cD_{k}$ are the restrictions of the layer potentials
$\bS_{k}$ and $\bD_{k}$ on the boundary $\Gamma$ respectively, and are given
by
\begin{align}
  \cS [\bmu] (\xx) &= \int_\Gamma \GG (\xx,\yy) \bmu(\yy)
  \, dS(\yy) \\
  \cD [\bmu] (\xx) &= \pv \int_\Gamma \left ( \TT_{\cdot,\cdot,\ell}(\bx,\by)
  \nu_\ell(\yy)
  \right )^\intercal \bmu(\yy) \, dS(\yy) \; .
\end{align}
Here \pv indicates that the integral is to be
evaluated in the principal value sense.
The integral equation~\cref{eq:inteq0} is known to be rank-deficient
for all values of $k$ due to the divergence-free condition
on $\bu$, and a standard approach is to use the following integral 
equation instead

\begin{equation}
\label{eq:inteq}
(\cI - 2\cD_{k} -2i \eta \cS_{k}-2\cW)\bmu = 0 \, \quad \textrm{on} \quad \Gamma \,,
\end{equation}
where $\cW$ is the operator given by
\begin{equation}
\cW[\bmu](\bx) = \frac{\bnu(x)}{|\Gamma|}\int_{\Gamma} \bmu(\by) \cdot \bnu(\by) \, ds \, .
\end{equation}

In~\cite{askhameig2019}, the authors show that the operator 
$\cI -2\cD_{k} -2i \cS_{k} -2\cW$ is not invertible if and only
if $k^2$ is a Stokes eigenvalue.
Furthermore if $\bmu$ is a non-zero null-vector of $\cI - 2\cD_{k} -2i \cS_{k} 
-2 \cW$, then 
$\bu = (i \eta \bS_{k} + \bD_{k})[\bmu]$ is the Stokes eigenfunction.

In order to verify the conditions in~\cref{lem:mainlem}, we
need to be able to compute the stream function associated with
the velocity $\bmu$ defined above.
If $\bmu = \mu_{\tau} \btau + \mu_{\nu} \bnu$, where $\btau=\bnu^{\perp}$
is the positively oriented tangential vector then the
layer potentials $\bS_{k}[\bmu]$ and $\bD_{k}[\bmu]$ can be rewritten as
\begin{align}
\bS_{k}[\bmu] &=  
\nabla^{\perp} 
\int_{\Gamma} (\partial_{\tau} \Gbh(\xx,\yy) \mu_{\tau}(\yy) -
\partial_{\nu} \Gbh(\xx,\yy) \mu_{\nu}(\yy)) \, ds \\
\bD_{k}[\bmu] &= 
-\nabla 
\int_{\Gamma} \Glap(\xx,\yy) \mu_{\nu}(\yy) \, ds 
+ \nabla^{\perp} 
\int_{\Gamma} \big( 2 \partial_{\nu\tau} \Gbh(\xx,\yy) \mu_{\nu}(\yy) 
+ \\
& \hspace*{35ex}(\partial_{\tau\tau} -\partial_{\nu\nu})\Gbh(\xx,\yy) \mu_{\tau}(\yy) 
\big) \, ds \, .
\end{align}

From the expressions above, it is clear that the stream function 
$\psi_{S}[\bmu]$ associated with the single layer potential is given
by
\begin{equation}
\psi_{S}[\bmu] = 
\int_{\Gamma} (\partial_{\tau} \Gbh(\xx,\yy) \mu_{\tau}(\yy) -
\partial_{\nu} \Gbh(\xx,\yy) \mu_{\nu}(\yy)) \, ds \, . 
\end{equation}

The situation with the double layer potential is a little trickier. 
We write the double layer potential as $\bD_{k}[\bmu] = \nabla \phi_{D}[\bmu]
+ \nabla^{\perp} \xi_{D}[\bmu]$, 
where 
\begin{align}
\label{eq:phiddef}
\phi_{D}[\bmu] &= 
-\int_{\Gamma} \Glap(\xx,\yy) \mu_{\nu}(\yy) \, ds  \, , \\
\xi_{D}[\bmu] &= 
\int_{\Gamma} \big( 2 \partial_{\nu\tau} \Gbh(\xx,\yy) \mu_{\nu}(\yy) 
+ (\partial_{\tau\tau} -\partial_{\nu\nu})\Gbh(\xx,\yy) \mu_{\tau}(\yy) ) \,
ds \, . 
\end{align}

If we can find a function $\tilde{\psi}_{D}[\bmu]$ such
that 
\begin{equation}
\label{eq:perptogradperp}
\nabla^{\perp} \tilde{\psi}_{D}[\bmu] = \nabla \phi_{D} [\bmu] \, ,
\end{equation}
then the stream function $\psi_{D}[\bmu]$ 
associated with the double layer potential would
be given by $\psi_{D}[\bmu] = \tilde{\psi}_{D}[\bmu] + \xi_{D}[\bmu]$.
However, on multiply connected domains, it is not necessarily true, 
that given a function $\phi_{D}[\bmu]$ of the form~\cref{eq:phiddef} 
there exists a single valued function $\tilde{\psi}_{D}[\bmu]$ 
which satisfies the condition~\cref{eq:perptogradperp} for
every $\bmu$.
Turns out, in the case where $\bmu$ satisfies the conditions
\begin{equation}
\label{eq:inteqconst}
\int_{\Gamma_{i}} \mu_{\nu} \, ds = 0 \, ,\quad i=0,1,2\ldots m \, ,
\end{equation}
then there exists a single valued function $\tilde{\psi}_{D}[\bmu]$
which satisfies~\cref{eq:perptogradperp} (see~\cite{rachh2015integral}, 
for example).
In the following lemma, we show that every null-vector of 
$\cI - 2\cD_{k} -2i \eta \cS_{k} - 2\cW$ satisfies the above integral
constraints.

\begin{lem}
Suppose $\bmu$ is a null-vector of 
$\cI - 2\cD_{k} - 2i \eta \cS_{k} -2\cW$, then
$\bmu$ satisfies~\cref{eq:inteqconst}.
\end{lem}
\begin{proof}
Insert proof here
\end{proof}
